Test-driven Knowledge Graph Construction

### 2023-05-06 doc/paper4.tex
Capitalize section headings

\section{Related work}
When outlining this method, we can learn from ontology engineering, as it has a head start of several decades on knowledge graphs. There is a long tradition of using competency questions as requirements for ontologies \cite{Gruninger1994}. Much of this experience can be reused, since ontologies serve as essential building blocks of knowledge graphs imbuing them with explicit semantics. Knowledge graphs in turn can be considered as ontologies populated with data. Creating tests for ontologies out of CQs is also nothing new \cite{Ren2014,Zemmouchi2013}. More recently, it was adopted for knowledge graphs too \cite{Pan2017}.

@@

\section{Non-functional requirements}
Note that the above-described method tests if a knowledge graph meets the given user requirements. It does not evaluate how well these requirements are satisfied. Absence of errors does not imply that the knowledge graph is sound. Therefore, the functional user requirements should be complemented by non-functional requirements describing the desired qualities of the solution. These requirements can be checked and refactored by using alternative sources of feedback, such as:

@@

\section{Case study: Antigen covid tests knowledge graph}

>>>>

\section{Related Work}
When outlining this method, we can learn from ontology engineering, as it has a head start of several decades on knowledge graphs. There is a long tradition of using competency questions as requirements for ontologies \cite{Gruninger1994}. Much of this experience can be reused, since ontologies serve as essential building blocks of knowledge graphs imbuing them with explicit semantics. Knowledge graphs in turn can be considered as ontologies populated with data. Creating tests for ontologies out of CQs is also nothing new \cite{Ren2014,Zemmouchi2013}. More recently, it was adopted for knowledge graphs too \cite{Pan2017}.

@@

\section{Non-functional Requirements}
Note that the above-described method tests if a knowledge graph meets the given user requirements. It does not evaluate how well these requirements are satisfied. Absence of errors does not imply that the knowledge graph is sound. Therefore, the functional user requirements should be complemented by non-functional requirements describing the desired qualities of the solution. These requirements can be checked and refactored by using alternative sources of feedback, such as:

@@

\section{Case Study: Antigen Covid Tests Knowledge Graph}
